How Safe is Campas Really? Assault Rate Trends Within and Around the University of Toronto: A Ten-Year Analysis

### 2024-01-24 outputs/paper/paper.qmd
Added some comments and my conclusion.

knitr::include_graphics("/cloud/project/inputs/sketches/uoft_neighbourhoods.png")
```

@@

knitr::include_graphics("/cloud/project/inputs/sketches/surrounding_neighbourhoods.png")
```

@@

# Plot the graph
ggplot(long_data, aes(x = Year, y = Assault_Rate, group = Neighbourhood, color = Neighbourhood)) +
  geom_line() +
  geom_point() +
  theme_minimal() +
  labs(
    title = "Assault Rates in University of Toronto 
      Neighbourhoods (2014-2023)",
    x = "Year",
    y = "Assault Rate",
    color = "Neighbourhood"
  ) +
  ylim(0, 3000) # Adjust these values based on your data's range

@@

>>>>

# Adding my map of UofT neighbourhoods
knitr::include_graphics("/cloud/project/inputs/sketches/uoft_neighbourhoods.png")
```

@@

# Adding my map of surrounding neighbourhoods
knitr::include_graphics("/cloud/project/inputs/sketches/surrounding_neighbourhoods.png")
```

@@

# Plot the graph
ggplot(long_data, aes(x = Year, y = Assault_Rate, group = Neighbourhood, color = Neighbourhood)) +
  geom_line() +
  geom_point() +
  theme_minimal() +
  labs(
    title = "Assault Rates in University of Toronto 
      Neighbourhoods (2014-2023)",
    x = "Year",
    y = "Assault Rate",
    color = "Neighbourhood"
  ) +
  ylim(0, 3000) # Adjust these values based on my data's range

@@

# Conclusion
This analysis of assault rates from 2014 to 2023 in and around the University of Toronto offers a unique view of campus safety in raletion to assault rates and its surrounding environment. The significant findings challenge the commonly held belief that university campuses, especially prestigious ones like the University of Toronto, are insulated and often safer then surrounding areas. The data shows a notable increase in assault rates in the "University" and "Annex" neighborhoods, areas predominantly associated with the University of Toronto. This upward trend, particularly since 2020, emphasizes the necessity for a reassessment of the current safety measures and policies in place on campus. The contrasting stability or minor fluctuations in assault rates in the surrounding neighborhoods further accentuates the specific challenges faced within the university's immediate vicinity. This analysis contributes to the dialogue around campus safety. The findings suggest that the University of Toronto might benefit from increased targeted interventions in relation to assault prevention and protection.
